### 2019-06-25 sections/language.tex
Removed all mention of clearing editors
Todo's from reviews

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed} or \emph{emptied}.
Empty editors can be \emph{filled}.

@@

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety.
Without type annotations, it would be possible to change the type of an editor, by clearing it and filling it with a value of different type.

@@

>>>>

\todo{Speaking about references you say "so they do not introduce implicit recursion (T-Update)". What do you want to mean by "implicit recursion". Is it because in the other cases $\tau$ can be again a Task and here $\beta$ can only be a basic type?}

@@

Programs in \TOPHAT model interactive workflows.
Interaction means communication with end users.
End users should be able to enter information into the system, change it, clear it, reenter it, and so on.
To do this, we introduce the concept of \emph{editors}.
%
Editors are typed containers that either hold a value or are empty.
Editors that have a value can be \emph{changed}.
Empty editors can be \emph{filled}.

@@

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety.

\todo{"Without type annotations, it would be possible to change the type of an editor, by clearing it and filling it with a value of different type." Is this a hypothetical affirmation (for the case the language wasn't type-safe) or a current feature of the language?}

@@

\end{example}
\todo{The starting double-quotes around 'Batman' and 'Na' are backwards.}

### 2019-06-25 sections/semantics.tex
Removed all mention of clearing editors
Todo's from reviews

The split between striding and normalisation is due to mutable references.
Consider the following example, where $\sigma=\set{l\mapsto\False}$.
\begin{TASK}
  (update l >>= \x:Bool. if x then e else fail) <&> (l := True; edit <<>>)
\end{TASK}
\pagebreak[2]
\refrule{S-And} reduces this expression in one step to
\begin{TASK}
  (update l >>= \x:Bool. if x then e else fail) <&> (edit <<>>)
\end{TASK}
with $\sigma'=\set{l\mapsto\True}$.
This expression is not normalised, because the left task can take a step.
The issue here lies in the fact that the right task updates $l$.
To overcome this problem, the \refrule{N-Done} and \refrule{N-Repeat} rules ensure that striding is applied until the state $\sigma$ becomes stable and no further normalisation can take place.
%XXX: Alejandro: The example is not 100\% clear to me

@@

\begin{figure}[h]
  \small
  \usemacro{O-Inputs-Compact}
  \caption{Inputs} \label{fig:observation-input}
\end{figure}

Handling input is done by the \emph{handling} semantics shown in \cref{fig:handling-semantics}.
It is a small step semantics with labelled transitions.
It takes a task $t$ in a state $\sigma$ and an input $i$, and yields a new task $t'$ in a new state $\sigma'$.

@@

  \paragraph{Editing}
  \begin{gather*}
    \userule{H-Change} \Quad
    \userule{H-Empty} \Break
    \userule{H-Fill} \Quad
    \userule{H-Update}
  \end{gather*}

@@

%FIXME: Revert rule names in front to normal sentences?
\refrule{H-Change},
\refrule{H-Empty},
\refrule{H-Fill},
\refrule{H-Update}:
Input events $v$ and $\Empty$ are used to change the value of editors and empty them.
Editors only accept values of the correct type.

>>>>

The split between striding and normalisation is due to mutable references.
Consider the following example, where $\sigma=\set{l\mapsto\False}$.
\begin{TASK}
  (update l >>= \x:Bool. if x then e else fail) <&> (l := True; edit <<>>)
\end{TASK}
\pagebreak[2]
\refrule{S-And} reduces this expression in one step to
\begin{TASK}
  (update l >>= \x:Bool. if x then e else fail) <&> (edit <<>>)
\end{TASK}
with $\sigma'=\set{l\mapsto\True}$.
\todo{you mention S-AND before having introduced the striding semantics (perhaps add a reference to the figure where this rule appears).}
This expression is not normalised, because the left task can take a step.
The issue here lies in the fact that the right task updates $l$.
To overcome this problem, the \refrule{N-Done} and \refrule{N-Repeat} rules ensure that striding is applied until the state $\sigma$ becomes stable and no further normalisation can take place.
%XXX: Alejandro: The example is not 100\% clear to me

@@

\begin{figure}[h]
  \small
  \usemacro{O-Inputs-Compact}
  \caption{Inputs} \label{fig:observation-input}
\end{figure}
\todo{when you write $v' : \tau$ (in the set comprehensions) I assume the intention is to say any input value of type $\tau$. I would write it as ${v' | v' : \tau}$.}
Handling input is done by the \emph{handling} semantics shown in \cref{fig:handling-semantics}.
It is a small step semantics with labelled transitions.
It takes a task $t$ in a state $\sigma$ and an input $i$, and yields a new task $t'$ in a new state $\sigma'$.

@@

  \paragraph{Editing}
  \begin{gather*}
    \userule{H-Change} \Quad
    \userule{H-Fill} \Break
    \userule{H-Update}
  \end{gather*}

@@

%FIXME: Revert rule names in front to normal sentences?
\refrule{H-Change},
\refrule{H-Fill},
\refrule{H-Update}:
Input events $v$ are used to change the value of editors.
Editors only accept values of the correct type.
